Optimizing the power of adaptive seamless designs using Bayesian Optimization

### 2020-10-05 main.tex
update plots

\begin{figure}[ht]
\centering
\begin{tikzpicture}[auto,node distance=1cm,align=center,text width = 3cm, inner sep = 0.1cm, font=\scriptsize, outer sep= 0cm]
  \node[draw, ellipse, minimum height=1cm, text width=2cm] (ClinicalScenarios) at (0,0) {
    \textbf{Clinical scenarios}\\
    Simulation Studies};
  \node[name=block, rectangle split, rectangle split parts=2, draw, above = of ClinicalScenarios] (UnknownPoints)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Treatment effect on early interim outcome.
      \item Treatment effect on late disability outcome
    \end{itemize}
    \nodepart{second} Unknown
  };
  \node[name=block, rectangle split, rectangle split parts=2, draw, anchor = north east] (HistoricalDataPoints) at (UnknownPoints.north west)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Correlation between early interim and late disability outcomes.
    \end{itemize}
    \nodepart{second} Historical data
  };
  %\node[draw, inner xsep=1em, inner ysep=1em, above left = of ClinicalScenarios, fit = (HistoricalDataPoints) (UnknownPoints)] (boxDiseaseSpecific) {};
  \node[draw, text width = 6.2cm, anchor = south west] (DiseaseSpecific) at (HistoricalDataPoints.north west) {\textbf{Disease-specific features}};
  %\node[draw, above right = of ClinicalScenarios] (DesignOptions) {Design options};
  \node[name=block, rectangle split, rectangle split parts=2, draw, anchor = north west] (ConstrainedPoints) at ([xshift = 4cm]HistoricalDataPoints.north east)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Number of test treatments
      \item Total subjects in trial
      \item recruitment rate
    \end{itemize}
    \nodepart{second} Constrained by health care environment/infrastructure
  };
  \node[name=block, rectangle split, rectangle split parts=2, draw, anchor = north west] (CombinationPoints) at (ConstrainedPoints.north east)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Adaptive seamless design time point of interim analysis
      \item Treatment selection rules at interim Conventional phase 2/3
      \item split of resources between phases
      \item end oh phase futility criteria
    \end{itemize}
    \nodepart{second} Combination of options
  };
  \node[draw,text width = 6.2cm, anchor = south west] (DesignOptions) at (ConstrainedPoints.north west) {\textbf{Design Options}};
  \node[draw, below = 0.5cm of ClinicalScenarios] (DesignPerformance) {
    \textbf{Design performance} \\ e.g.\ statistical power};
  \node[draw, right = of DesignPerformance, text width = 4cm, node distance = 2cm] (Evaluation) {
    \textbf{Clinical Scenario Evaluation}\\
    Design performance measures evaluated across a wide range of clinical scenarios};
  \draw[->] (HistoricalDataPoints) -- (ClinicalScenarios);
  \draw[->] (UnknownPoints) -- (ClinicalScenarios);
  \draw[->] (CombinationPoints) -- (ClinicalScenarios);
  \draw[->] (ConstrainedPoints) -- (ClinicalScenarios);
  \draw[->] (ClinicalScenarios) -- (DesignPerformance);
  \draw[->] (DesignPerformance) -- (Evaluation);
\end{tikzpicture}
%FIXME Is this the right paper? Convert to tikz! Tim schickt mir das Original!
%Friede et al (2010) DIJ, Figure 2 https://link.springer.com/content/pdf/10.1177/009286151004400507.pdf? https://link.springer.com/content/pdf/10.1177/009286151004400607.pdf
\caption{Application of the refined clinical scenario evaluation framework to adaptive seamless designs in progressive multiple sclerosis.}
\label{fig:friede_refinement_2010_fig2}
\end{figure}

@@

As explained before, we obtained unbiased result from the exhaustive grid search and the MBO procedure.
However, in Figure~\ref{fig:plot_allbest} we show the observed outcomes during evaluation of the grid as well as the final configurations found by MBO, to demonstrate the behaviour of the simulation in dependence of the parameters \emph{selection strategy} and \emph{stage ratio}.
\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_allbest.pdf}
\caption{Power of the different selection rules. For the epsilon and threshold rule only the curve for the epsilon and threshold value that reached the best power is dispayed.}
\label{fig:plot_allbest}
\end{figure}
Note that the \emph{stage ratio} is not drawn directly but the resulting number of treatments at the early stage.
Also, for the \emph{selection strategy} \emph{epsilon rule} and \emph{threshold rule} only the curves are shown of the repsective \emph{eps} and \emph{thresh} value that led to the best outcome within the respective selection strategy.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_opt_path.pdf}
\caption{%
  Optimization curves of each optimization run and the mean of all runs drawn as a black line.
  }
\label{fig:plot_opt_path} 
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}[auto,node distance=1cm,align=center,text width = 3cm, inner sep = 0.1cm, font=\sffamily \scriptsize, outer sep= 0cm]
  \node[draw, ellipse, minimum height=1cm, text width=2.5cm] (ClinicalScenarios) at (0,0) {
    \textbf{Clinical scenarios}\\
    Simulation Studies};
  \node[name=block, rectangle split, rectangle split parts=2, draw, above = of ClinicalScenarios] (UnknownPoints)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Treatment effect on early interim outcome.
      \item Treatment effect on late disability outcome
    \end{itemize}
    \nodepart{second} Unknown
  };
  \node[name=block, rectangle split, rectangle split parts=2, draw, anchor = north east] (HistoricalDataPoints) at (UnknownPoints.north west)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Correlation between early interim and late disability outcomes.
    \end{itemize}
    \nodepart{second} Historical data
  };
  %\node[draw, inner xsep=1em, inner ysep=1em, above left = of ClinicalScenarios, fit = (HistoricalDataPoints) (UnknownPoints)] (boxDiseaseSpecific) {};
  \node[draw, text width = 6.2cm, anchor = south west] (DiseaseSpecific) at (HistoricalDataPoints.north west) {\textbf{Disease-specific features}};
  %\node[draw, above right = of ClinicalScenarios] (DesignOptions) {Design options};
  \node[name=block, rectangle split, rectangle split parts=2, draw, anchor = north west] (ConstrainedPoints) at ([xshift = 4cm]HistoricalDataPoints.north east)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Number of test treatments
      \item Total subjects in trial
      \item recruitment rate
    \end{itemize}
    \nodepart{second} Constrained by health care environment/infrastructure
  };
  \node[name=block, rectangle split, rectangle split parts=2, draw, anchor = north west] (CombinationPoints) at (ConstrainedPoints.north east)
  { \begin{itemize}[leftmargin=.3cm, topsep=0cm,itemsep=0cm,partopsep=0cm, parsep=0cm]
      \item Adaptive seamless design time point of interim analysis
      \item Treatment selection rules at interim Conventional phase 2/3
      \item split of resources between phases
      \item end oh phase futility criteria
    \end{itemize}
    \nodepart{second} Combination of options
  };
  \node[draw,text width = 6.2cm, anchor = south west] (DesignOptions) at (ConstrainedPoints.north west) {\textbf{Design Options}};
  \node[draw, below = 0.5cm of ClinicalScenarios] (DesignPerformance) {
    \textbf{Design performance} \\ e.g.\ statistical power};
  \node[draw, right = of DesignPerformance, text width = 4cm, node distance = 2cm] (Evaluation) {
    \textbf{Clinical Scenario Evaluation}\\
    Design performance measures evaluated across a wide range of clinical scenarios};
  \draw[->] (HistoricalDataPoints) -- (ClinicalScenarios);
  \draw[->] (UnknownPoints) -- (ClinicalScenarios);
  \draw[->] (CombinationPoints) -- (ClinicalScenarios);
  \draw[->] (ConstrainedPoints) -- (ClinicalScenarios);
  \draw[->] (ClinicalScenarios) -- (DesignPerformance);
  \draw[->] (DesignPerformance) -- (Evaluation);
\end{tikzpicture}
%FIXME Is this the right paper? Convert to tikz! Tim schickt mir das Original!
%Friede et al (2010) DIJ, Figure 2 https://link.springer.com/content/pdf/10.1177/009286151004400507.pdf? https://link.springer.com/content/pdf/10.1177/009286151004400607.pdf
\caption{Application of the refined clinical scenario evaluation framework to adaptive seamless designs in progressive multiple sclerosis.}
\label{fig:friede_refinement_2010_fig2}
\end{figure}

@@

As explained before, we obtained unbiased result from the exhaustive grid search and the MBO procedure.
However, in Figure~\ref{fig:plot_allbest} we show the observed outcomes during evaluation of the grid as well as the final configurations found by MBO, to demonstrate the behaviour of the simulation in dependence of the parameters \emph{selection strategy} and \emph{stage ratio}.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_allbest.pdf}
\caption{Power of the different selection rules. For the epsilon and threshold rule only the curve for the epsilon and threshold value that reached the best power is dispayed.}
\label{fig:plot_allbest}
\end{figure}
Note that the \emph{stage ratio} is not drawn directly but the resulting number of treatments at the early stage.
Also, for the \emph{selection strategy} \emph{epsilon rule} and \emph{threshold rule} only the curves are shown of the repsective \emph{eps} and \emph{thresh} value that led to the best outcome within the respective selection strategy.

@@
